---
title: "Alcohol vs Seat choice"
author: "Isai Bercian"
date: "Spring 2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r include=FALSE}
require(tidyverse)
require(tigerstats)
davisdata <- read.csv(file="UCDavis.csv") 
```
 Our Goal is to answer this question Is there a difference between the alcohol consumed between the row
 you choose to sit in??

## Now with ggplot - first select the basic data


   ```{r}
basicCN <- ggplot(davisdata,aes(y=alcohol,x=Seat))
```
## Now add in boxplot

```{r}
basicCN + geom_boxplot()
```
  
  
### get fancy  

```{r}
basicCN + geom_boxplot(notch=TRUE,outlier.color = "red") + stat_boxplot(geom ='errorbar') + labs(title="Fancy notch boxplot \n with 2 lines")
```


This BoxPlot shows that the heavy drinkers are mostly in the back.

## Numerical Summarys 

```{r}
favstats(alcohol~Seat,data=ucdavis1)
```

People who sit in the back drink three times as much alcohol then the people who sit in the front or in the middle by an enormous amount.

## Inferential Tests

# Inferential

```{r}
model1 <- aov(alcohol~Seat,data=davisdata)
summary.aov(model1)
```
The P value is so small that it's unlikely that the alcohol consumption in the front middle and back are the same.

## When significant follow up with TukeyHSD  

```{r}
plot(TukeyHSD(model1))
```
The TurkyHSD plot shows that the people in the back drink a lot more then the people in the front; It shows that the people in the middle drink less then the people in the back; The Middle-Front shows no evidence of difference than the average alcohol consumption.
## Conclusions

The evidence shows that most people that consume alcohol tend to sit in the back of the class 
